An Open Platform for Managing Short Programming Exercises

### 2013-06-25 paper/paper.tex
editing to avoid a bad section break

Our primary motivation in developing CloudCoder
was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that locking down either
the software or the exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.

@@

CloudCoder is available under the GNU Affero General Public License\cite{AGPL}.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on GitHub:
\begin{quote}
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\end{quote}

@@

CloudCoder supports two types of exercises:  {\em function-based}
exercises and {\em whole-program} exercises.  Function-based exercises are
very similar to CodingBat exercises: the student is required to write
a function (or method, depending on the programming language) that takes some number of parameter values,
does a computation, and returns a result value.
Students are given a description of
what the function should do, and a couple of example inputs with
expected results.  Writing a new function-based exercise
requires a description, some skeleton code (typically the method
header, although exercises can provide as much or as little code as
desired), and a series of inputs and their corresponding expected results.
Test cases can be marked as ``secret'' so that students don't see the
inputs or expected results, to discourage students from writing a special case to
recognize each input.

@@

This work was supported by a SIGCSE Special Projects grant (May 2012),
a York College Summer Research Fellowship (Summer 2013), an award from
the Paul K Richter and Evalyn E. Cook Richter Memorial Trusts at Knox
College, and an Amazon Web Services Teaching Grant.

>>>>

Our primary motivation in developing CloudCoder,
a new programming exercise system,
was {\em freedom}: we wanted a system where
the software and exercises could be freely redistributed, and
were not under the control of any central authority.  This motivation
is not entirely philosophical: we felt that locking down either
the software or the exercises would result in a barrier to adoption,
limiting the potential impact of the system.
As we will discuss in Section~\ref{sec:questions}, we think that there
are some interesting research questions that can be addressed
best through the existence of a ``free like air'' programming
exercise system: for example, we are interested in finding out
whether exercises can be reused effectively in different courses
at different institutions.

@@

CloudCoder's source code is available under the GNU Affero General Public License\cite{AGPL}.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on GitHub:
\begin{quote}
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\end{quote}

@@

CloudCoder supports two types of exercises:  {\em function-based}
exercises and {\em whole-program} exercises.  Function-based exercises are
very similar to CodingBat exercises: the student is required to write
a function (or method, depending on the programming language) that takes some parameter values,
does a computation, and returns a result value.
Students are given a description of
what the function should do, and a couple of example inputs with
expected results.  Writing a new function-based exercise
requires a description, some skeleton code (typically the method
header, although exercises can provide as much or as little code as
desired), and a series of inputs and their corresponding expected results.
Test cases can be marked as ``secret'' so that students don't see the
inputs or expected results, to discourage students from writing a special case to
recognize each input.

@@

This work was supported by a SIGCSE Special Projects grant (May 2012),
a York College Summer Research Fellowship (Summer 2013), an award from
the Paul K.\ Richter and Evalyn E.\ Cook Richter Memorial Trusts at Knox
College, and an Amazon Web Services Teaching Grant.
